
\documentclass[8pt]{extarticle}
\usepackage{amssymb,amsmath,amsthm,amsfonts}
\usepackage{multicol,multirow}
\usepackage{calc}
\usepackage{ifthen}
\usepackage[a4paper, landscape]{geometry}
\usepackage[hidelinks,colorlinks=false]{hyperref}
\usepackage{tcolorbox}
\usepackage{graphicx}
\usepackage{tikz}
\usetikzlibrary{arrows.meta,
    positioning,
    quotes, shapes, spy, matrix}
\usepackage[percent]{overpic}
\usepackage{../wnm-latex-utils}
\usepackage{ragged2e}
\usepackage{amssymb}

\geometry{top=0.7cm,left=0.7cm,right=0.7cm,bottom=0.7cm}

\makeatletter
\makeatother
\setcounter{secnumdepth}{0}
\setlength{\parindent}{0pt}
\setlength{\parskip}{0pt plus 0.5ex}

\begin{document}

\raggedright
\footnotesize

\justifying

\begin{multicols*}{3}
\setlength{\premulticols}{1pt}
\setlength{\postmulticols}{1pt}
\setlength{\multicolsep}{1pt}
\setlength{\columnsep}{2pt}

\section{Compliance and Safety Information (en)}

\subsection{Warnings}
\begin{itemize}
\item To prevent possible hearing damage, do not listen at high sound levels for long periods.
\item This product shall only be connected to an external USB power supply rated at 5V dc, and a minimum current of 500mA. Any external power supply used with the PGB-1 shall comply with relevant regulations and standards applicable in the country of intended use.
\item Risk of explosion or fire if the battery is replaced by an incorrect type. Any replacement battery used with the PGB-1 shall comply with relevant regulations and standards applicable in the country of intended use.
\item All peripherals used should comply with relevant standards for the country of use and be marked accordingly to ensure that safety and performance requirements are met.
\item When peripherals are connected, the cable used must offer adequate insulation and operation in order to meet the relevant performance and safety requirements.
\item Modifications not expressly approved by Wee Noise Makers could void the user’s authority to operate the equipment.
\end{itemize}

\subsection{Instructions for safe use}

To avoid malfunction or damage to your PGB-1 please observe the following:
\begin{itemize}
\item Do not expose it to water, moisture.
\item Do not expose it to extremes of heat or cold. PGB-1 is designed for reliable operation at normal ambient room temperatures.
\item Do not drop or hit. Doing so may damage the screen or other components.
\item Do not expose the battery to excessive physical shock, vibration, or liquids.
\item Do not disassemble, attempt to repair, or deform the battery.
\item Do not dispose of batteries in a fire.
\item Do not touch the terminals of the battery or cause a short between the terminals with a metal object.
\item Take care to protect the screen from scratches or stains.
\end{itemize}

\subsection{Regulatory Information}

\subsubsection{The FCC Wants You to Know}

This equipment has been tested and found to comply with the limits for a Class B digital device, pursuant to Part 15 of the FCC rules. These limits are designed to provide reasonable protection against harmful
interference in a residential installation. This equipment generates, uses and can radiate radio frequency
energy and, if not installed and used in accordance with the instructions, may cause harmful interference to radio communications. However, there is no guarantee that interference will not occur in a particular
installation. If this equipment does cause harmful interference to radio or television reception, which can be determined by turning the equipment off and on, the user is encouraged to try to correct the interference by one or more of the following measures:
\begin{itemize}
\item Reorient or relocate the receiving antenna.
\item Increase the separation between the equipment and receiver.
\item Connect the equipment to an outlet on a circuit different from that to which the receiver is connected.
\item Consult the dealer or an experienced radio/TV technician.
\end{itemize}

\subsubsection{FCC Warning}

Wee Noise Makers has not approved any changes or modifications to this device by the user. Any
changes or modifications could void the user's authority to operate the equipment.

\subsubsection{Interference statement}

This device complies with Part 15 of the FCC Rules. Operation is subject to the following two conditions: (1) this device may not cause interference, and (2) this device must accept any interference, including interference that may cause undesired operation of the device.

%\vfill\null
%\columnbreak

\section{Informations sur la conformité et la sécurité  (fr)}

\subsection{Avertissements}
\begin{itemize}
\item Pour éviter d'éventuels dommages auditifs, n'écoutez pas à des niveaux sonores élevés pendant de longues périodes.
\item Ce produit doit être connecté uniquement à une alimentation USB externe de 5 V CC et d'un courant minimal de 500 mA. Toute alimentation externe utilisée avec le PGB-1 doit être conforme aux réglementations et normes en vigueur dans le pays d'utilisation prévu.
\item Risque d'explosion ou d'incendie en cas de remplacement de la batterie par un modèle incorrect. Toute batterie de remplacement utilisée avec le PGB-1 doit être conforme à la réglementation et aux normes en vigueur dans le pays d'utilisation prévu.
\item Tous les périphériques utilisés doivent être conformes aux normes en vigueur dans le pays d'utilisation et être marqués en conséquence afin de garantir que les exigences de sécurité et de performance sont respectées.
\item Lors de la connexion de périphériques, le câble utilisé doit offrir une isolation et un fonctionnement adéquats afin de répondre aux exigences de performance et de sécurité pertinentes.
\item Les modifications non expressément approuvées par Wee Noise Makers pourraient annuler le droit de l'utilisateur à utiliser l'équipement.
\end{itemize}

\subsection{Instructions pour une utilisation en toute sécurité}

Pour éviter tout dysfonctionnement ou dommage à votre PGB-1, veuillez respecter les consignes suivantes:
\begin{itemize}
\item Ne pas exposer à l'eau, à l'humidité.
\item Ne l'exposez pas à des températures extrêmes. Le PGB-1 est conçu pour un fonctionnement fiable à température ambiante normale.
\item Ne pas laisser tomber ni heurter l'appareil. Cela pourrait endommager l'écran ou d'autres composants.
\item N'exposez pas la batterie à des chocs physiques excessifs, à des vibrations ou à des liquides.
\item Ne démontez pas, ne tentez pas de réparer ou de déformer la batterie.
\item Ne jetez pas les piles au feu.
\item Ne touchez pas les bornes de la batterie et ne provoquez pas de court-circuit entre les bornes avec un objet métallique.
\item Prenez soin de protéger l'écran des rayures ou des taches.
\end{itemize}

\subsection{Informations réglementaires}

Avertissement

Wee Noise Makers n'a approuvé aucune modification apportée à cet appareil par l'utilisateur. Toute modification pourrait annuler le droit de l'utilisateur à utiliser l'équipement.

\vfill\null
\columnbreak

\section{Compliance und Sicherheitsinformationen (de)}

\subsection{Warnungen:}
\begin{itemize}
\item Um möglichen Gehörschäden vorzubeugen, hören Sie nicht über längere Zeit mit hoher Lautstärke.
\item Dieses Produkt darf nur an ein externes USB-Netzteil mit 5 V Gleichstrom und einer Mindeststromstärke von 500 mA angeschlossen werden. Jedes mit dem PGB-1 verwendete externe Netzteil muss den geltenden Vorschriften und Normen des jeweiligen Landes entsprechen.
\item Es besteht Explosions- oder Brandgefahr, wenn die Batterie durch einen falschen Typ ersetzt wird. Jede mit dem PGB-1 verwendete Ersatzbatterie muss den einschlägigen Vorschriften und Normen des Landes entsprechen, in dem sie verwendet wird.
\item Alle verwendeten Peripheriegeräte sollten den relevanten Standards des jeweiligen Landes entsprechen und entsprechend gekennzeichnet sein, um sicherzustellen, dass die Sicherheits- und Leistungsanforderungen erfüllt werden.
\item Beim Anschluss von Peripheriegeräten muss das verwendete Kabel eine ausreichende Isolierung und Funktion bieten, um die entsprechenden Leistungs- und Sicherheitsanforderungen zu erfüllen.
\item Durch Änderungen, die nicht ausdrücklich von Wee Noise Makers genehmigt wurden, kann die Berechtigung des Benutzers zum Betrieb des Geräts erlöschen.
\end{itemize}

\subsection{Hinweise zur sicheren Verwendung}

Um Fehlfunktionen oder Schäden an Ihrem PGB-1 zu vermeiden, beachten Sie bitte Folgendes:
\begin{itemize}
\item Setzen Sie weder Wasser noch Feuchtigkeit aus.
\item Setzen Sie es keiner extremen Hitze oder Kälte aus. PGB-1 ist für einen zuverlässigen Betrieb bei normalen Raumtemperaturen ausgelegt.
\item Lassen Sie das Gerät nicht fallen und stoßen Sie es nicht an. Dadurch können der Bildschirm oder andere Komponenten beschädigt werden.
\item Setzen Sie die Batterie keinen übermäßigen Stößen, Vibrationen oder Flüssigkeiten aus.
\item Zerlegen Sie die Batterie nicht, versuchen Sie nicht, sie zu reparieren, und verformen Sie sie nicht.
\item Werfen Sie Batterien nicht ins Feuer.
\item Berühren Sie nicht die Anschlüsse der Batterie und verursachen Sie nicht mit einem Metallgegenstand einen Kurzschluss zwischen den Anschlüssen.
\item Achten Sie darauf, den Bildschirm vor Kratzern oder Flecken zu schützen.
\end{itemize}

\subsection{Regulatorische Informationen}

Warnung

Wee Noise Makers hat keine Änderungen oder Modifikationen an diesem Gerät durch den Benutzer genehmigt. Jegliche Änderungen oder Modifikationen können zum Erlöschen der Betriebserlaubnis führen.

%\vfill\null
%\columnbreak

\end{multicols*}

\end{document}